A Novel Model-Free Learning Approach for Dynamic Target Tracking Problem and its Validation using Virtual Robot Experimentation Platform

### 2020-06-29 paperMIC2020/paperIEEE-MIC2020-V1.tex
added the figure

\author{%~
\IEEEauthorblockN{Amr Elhussein and Md Suruz Miah}
\IEEEauthorblockA{\textit{Electrical \& Computer Eng.} \\
\textit{Bradley University}, Peoria, Illinois, USA \\
smiah@bradley.edu  and aelhussein@mail.bradley.edu}
% \and
% \IEEEauthorblockN{Fazel Keshtkar}
% \IEEEauthorblockA{\textit{Div. of Computer Science, Math. and Science} \\
% \textit{St John's University}, Queens, NY, USA \\
% keshtkaf@stjohns.edu}
% \and
% \IEEEauthorblockN{Mohammed Abouheaf}
% \IEEEauthorblockA{\textit{School of EECS} \\
% \textit{Univ. of Ottawa}, Canada\\
% mabouhea@uottawa.ca}
%
}

@@

\comment{This paper advances the previous work done by authors by validating a model-free actor-critic reinforcement learning approach to solve dynamic target tracking problem for a car-like mobile robot. The learning approach generates the linear velocity and steering angle of the robot and it does not require any prior knowledge of the dynamic model of the moving target. Policy iteration approach is employed through Bellman's principle of optimality to assess the cost of the control actions derived by the proposed learning method. The algorithm is tested by coducting a set of computer expeeriments for complex secnarios using virtual robot expirementation platform widely known as CoppeliaSim.        
}{Need to be rewritten}  
%
\end{abstract}

@@

Suppose that a wheeled mobile robot (follower) with coordinate $(x,y)$ and orientation $\theta\in[-\pi,\pi)~\si{\radian}$ with respect to the global X-Y coordinate has a linear speed $\nu$ and steering angle $\gamma$ which are considered as the two control actions. Let the posistion and orientation (pose) of the target i.e leader be ${\bf q}_k\equiv[x_k,y_k,\theta_k]$. The robot and the target are deployed in a 2D configuration in which the Follower is to follow the target trajectory defined by  $(\mathbf{p}_k^{[\ell]})^T=[x_k^{[\ell]},y_k^{[\ell]}(t)]$ at time $t\ge 0$ with $t=k \, T_s,$ $k\in\mathbb{N}_0,$ and $T_s>0$ being the sampling time. Note that this trajectory is completley random. The target motion is modeled by the following discrete-time system:
 \begin{align}
   \label{eq:leaderDT}
   \mathbf{p}_{k+1}^{[\ell]} = \mathbf{p}_k^{[\ell]} + T_s \, \mathbf{u}_k^{[\ell]},
 \end{align}  
with $\mathbf{u}_k^{[\ell]}\in\mathbb{R}^2$ being the control inputs of the target movment. 
\\ The follower robot is to maintain a constant safe-distance $d>0$ from target. The dynamic car-like model of the follower robot is defined as follows:
  \begin{figure}
\todo[inline]{redraw figure and add coppelia sim figures}
   \centering
   \fcolorbox{gray!10}{gray!5}{
     \includegraphics[width=0.45\textwidth]{figs/ipe/LF-Setup}
`     }
   \caption{Mobile robot and its leader-follower problem setup.}
   \label{fig:leaderFollowerSetup}
 \end{figure}
 \begin{subequations}
   \begin{align}
     x_{k+1}& =x_{k}+T_s\nu_{k}\cos{(\theta_{k}+\gamma_{k})} + \zeta_1,\\  
     y_{k+1}& =y_{k}+T_s\nu_{k}\sin{(\theta_{k}+\gamma_{k})}+ \zeta_2,\\
     \theta_{k+1}&=\theta_{k}+T_s\nu_{k}\frac{\sin{(\gamma_{k})}}{l}+ \zeta_3,
   \end{align}
 \label{eq:robotModel1-DT}
 \end{subequations}
 \\
\hl{Note that the follower dynamic model obeys Ackermann steering principle where $\gamma_k\in(-\frac{\pi}{2},\frac{\pi}{2})$ is the front wheel steering angle with respect to the robot's orientation $\theta_k\in[-\pi,\pi),$ $\nu_k$ is the linear speed, $l$ is the distance between the drive wheels of the robot, and $\zeta_1,\zeta_2,\zeta_3\in\mathbb{R}$ are the model uncertainties.} 
\\
We then define the error vector as:
 \begin{multline}
     \label{eq:stateError}
   \mathbf{e}_k^T = [\sqrt{x_e^2-y_e^2},\theta_e]^T = \\
   \begin{bmatrix}
     \sqrt{(x_k^{[\ell]} - x_k - d\cos\theta_k^{'})^2-
     (y_k^{[\ell]} - y_k - d\sin\theta_k^{'})^2},
     \theta_k^{'} - \theta_k
   \end{bmatrix},
 \end{multline}

 where $\theta_k^{'} = \mathrm{atan2}\left(y_k^{[\ell]}-y_k, x_k^{[\ell]}-x_k\right).$  
\\
\hl{The control problem can then be formally stated as follows}: Find $\nu_k$ and $\gamma_k$ such that ${\bf e}_k\to {\bf 0}$ as  $k\to\infty$ subject to~\eqref{eq:leaderDT}~\text{and}~\eqref{eq:robotModel1-DT}.

>>>>

\author{%~
\IEEEauthorblockN{Amr Elhussein and Md Suruz Miah}
\IEEEauthorblockA{\textit{Electrical \& Computer Eng.} \\
\textit{Bradley University}, Peoria, Illinois, USA \\
 aelhussein@mail.bradley.edu and smiah@bradley.edu}
% \and
% \IEEEauthorblockN{Fazel Keshtkar}
% \IEEEauthorblockA{\textit{Div. of Computer Science, Math. and Science} \\
% \textit{St John's University}, Queens, NY, USA \\
% keshtkaf@stjohns.edu}
% \and
% \IEEEauthorblockN{Mohammed Abouheaf}
% \IEEEauthorblockA{\textit{School of EECS} \\
% \textit{Univ. of Ottawa}, Canada\\
% mabouhea@uottawa.ca}
%
}

@@

This paper advances the previous work done by authors by validating a model-free actor-critic reinforcement learning approach to solve dynamic target tracking problem for a car-like mobile robot. The learning approach generates the linear velocity and steering angle of the robot and it does not require any prior knowledge of the dynamic model of the moving target. Policy iteration approach is employed through Bellman's principle of optimality to assess the cost of the control actions derived by the proposed learning method. The algorithm is tested by coducting a set of computer experiments for complex secnarios using virtual robot expirementation platform widely known as CoppeliaSim.

\todo[inline]{Review and expand}  
%
\end{abstract}

@@

Suppose that a wheeled mobile robot (follower) with coordinate $(x,y)$ and orientation $\theta\in[-\pi,\pi)~\si{\radian}$ with respect to the global X-Y coordinate has a linear speed $\nu$ and steering angle $\gamma$ which are considered as the two control actions. Let the posistion and orientation (pose) of the target i.e leader be ${\bf q}_k\equiv[x_k,y_k,\theta_k]$. The robot and the target are deployed in a 2D configuration in which the Follower is to follow the target trajectory defined by  $(\mathbf{p}_k^{[d]})^T=[x_k^{[d]},y_k^{[d]}(t)]$ at time $t\ge 0$ with $t=k \, T_s,$ $k\in\mathbb{N}_0,$ and $T_s>0$ being the sampling time. Note that this trajectory is completley random. The target motion is modeled by the following discrete-time system:
 \begin{align}
   \label{eq:leaderDT}
   \mathbf{p}_{k+1}^{[d]} = \mathbf{p}_k^{[d]} + T_s \, \mathbf{u}_k^{[d]},
 \end{align}  
with $\mathbf{u}_k^{[\ell]}\in\mathbb{R}^2$ being the control inputs of the target movment. 
\\ The follower robot is to maintain a constant safe-distance $d>0$ from target. The dynamic car-like model of the follower robot is defined as follows:
  \begin{figure}
   \centering
   \fcolorbox{gray!10}{gray!5}{
     \includegraphics[width=0.45\textwidth]{figs/ipe/LFMICSetup.eps}
    }
   \caption{Mobile robot and its dynamic target tracking problem setup.}
   \label{fig:leaderFollowerSetup}
 \end{figure}
 \begin{subequations}
   \begin{align}
     x_{k+1}& =x_{k}+T_s\nu_{k}\cos{(\theta_{k}+\gamma_{k})} + \zeta_1,\\  
     y_{k+1}& =y_{k}+T_s\nu_{k}\sin{(\theta_{k}+\gamma_{k})}+ \zeta_2,\\
     \theta_{k+1}&=\theta_{k}+T_s\nu_{k}\frac{\sin{(\gamma_{k})}}{l}+ \zeta_3,
   \end{align}
 \label{eq:robotModel1-DT}
 \end{subequations}
 \\
\hl{Note that the follower dynamic model obeys Ackermann steering principle where $\gamma_k\in(-\frac{\pi}{2},\frac{\pi}{2})$ is the front wheel steering angle with respect to the robot's orientation $\theta_k\in[-\pi,\pi),$ $\nu_k$ is the linear speed, $l$ is the distance between the drive wheels of the robot, and $\zeta_1,\zeta_2,\zeta_3\in\mathbb{R}$ are the model uncertainties.} 
\\
We then define the error vector as:
 \begin{multline}
     \label{eq:stateError}
   \mathbf {e}_k^T = [\rho_e,\theta_e]^T =
   [\sqrt{x_e^2+y_e^2},\theta_e]^T = \\
   \begin{bmatrix}
     \sqrt{(x_k^{[d]} - x_k - d\cos\theta_k^{'})^2+
     (y_k^{[d]} - y_k - d\sin\theta_k^{'})^2},
     \theta_k^{'} - \theta_k
   \end{bmatrix},
 \end{multline}

 where $\theta_k^{'} = \mathrm{atan2}\left(y_k^{[d]}-y_k, x_k^{[d]}-x_k\right).$ and ${\rho_e}$ being the euclidean distance. 
\\
\hl{The control problem can then be formally stated as follows}: Find $\nu_k$ and $\gamma_k$ such that ${\bf e}_k\to {\bf 0}$ as  $k\to\infty$ subject to~\eqref{eq:leaderDT}~\text{and}~\eqref{eq:robotModel1-DT}.
